Insert the article title here

### 2018-04-04 writeup/manuscript.tex
Compiled Jess's edits.

The ACVS was based on the task described in Irons & Leber (2016), with a few changes [Or identical to the task described in Experiment 1 of Irons & Leber, in press by then hopefully].

Each search display was composed of 54 small squares (size? What was viewing distance & screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The inner ring was XX° and the outer ring was XX° from fixation. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”. Variable distractors changes colors afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change color from almost red to magenta (at the 4th trial in the transition) to almost blue (see Irons & Leber, 2017, for the specific color values? Or supplemental?). The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red. This 24-trial cycle would repeat throughout the entire experiment.

@@

The foraging task was based on Kristjansson, Johannesson & Thornton (2014) and Johannsesson et al (2016). Participants completed the feature foraging and conjunction foraging tasks on separate days, with the order counterbalanced (was it counterbalanced?).

>>>>

The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes [Or identical to the task described in Experiment 1 of Irons \& Leber, in press by then hopefully].

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”. Variable distractors changes colors afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change color from almost red to magenta (at the 4th trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific color values? Or supplemental?). The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red. This 24-trial cycle would repeat throughout the entire experiment.

@@

The foraging task was based on \cite{kristjansson2014} and \cite{johannesson2016}. Participants completed the feature foraging and conjunction foraging tasks on separate days, with the order counterbalanced (was it counterbalanced?).
